MergeBiomarkWith10X

### 2021-12-08 MergeBiomarkWith10X/MergeBiomarkWith10X.Rmd
Updated analyses

	cluster_ids <- sort(unique(tech.integrated@meta.data[,current_res]))
	counts_df <- data.frame(matrix(nrow = length(cluster_ids), ncol = 4))
	rownames(counts_df) <- cluster_ids
	colnames(counts_df) <- c("10X", "biomark", "pct10X", "pctbiomark")
	tot.10X <- nrow(tech.integrated@meta.data[tech.integrated@meta.data$orig.ident == "10X", ])
	tot.biomark <- nrow(tech.integrated@meta.data[tech.integrated@meta.data$orig.ident == "biomark", ])
	for(id in cluster_ids){
		cell_value <- nrow(tech.integrated@meta.data[(tech.integrated@meta.data[current_res] == id) & 
																								 	(tech.integrated@meta.data$orig.ident == "10X"),])
		counts_df[id, "10X"] = cell_value
		counts_df[id, "pct10X"] = round(cell_value/tot.10X*100, 2)
		cell_value <- nrow(tech.integrated@meta.data[(tech.integrated@meta.data[current_res] == id) & 
																								 	(tech.integrated@meta.data$orig.ident == "biomark"),])
		counts_df[id, "biomark"] = cell_value
		counts_df[id, "pctbiomark"] = round(cell_value/tot.biomark*100, 2)
	}
	try(xlsx::write.xlsx(x = counts_df, 
											 file = paste0(projectName, "_pctVar", pct.var, "_stats.xlsx"), 
											 sheetName = current_res, 
											 col.names = TRUE, 
											 row.names = TRUE, 
											 append = TRUE)
	)
	counts_df
}
```

@@

```{r}
fluor.cols <- names(mfi[, grepl("pos$", names(mfi))])
mfi.norm <- data.frame(matrix(nrow = 0, ncol = length(fluor.cols)))
colnames(mfi.norm) <- fluor.cols
for(sortdate in unique(mfi$sortdate)){
	mfi.subset <- scale(mfi[mfi$sortdate == sortdate, fluor.cols])
	mfi.norm <- rbind(mfi.norm, mfi.subset)
}
mfi.norm["pid"] <- do.call(rbind, strsplit(rownames(mfi.norm), '_'))[,3]
```
Add metadata column
```{r}
tech.integrated <- AddMetaData(tech.integrated, metadata = mfi.norm)
```
now plot some stuff
```{r}
biomark.integrated <- subset(tech.integrated, subset = orig.ident == "biomark")
```
```{r fig.height=12, fig.width=5}
RidgePlot(biomark.integrated, features = fluor.cols, cols = color.palette, ncol = 1)
```
```{r}
png(filename = paste0(projectName, "_pctVar", integrated.var, "res", integrated.res, "-fluor.png"), height = 2400, width = 800)
RidgePlot(biomark.integrated, features = fluor.cols, cols = color.palette, ncol = 1)
dev.off()
```
plot umaps
```{r}
for(integrated.col in integrated.ident.list){
		plot.title <- paste0(projectName, "_pctVar", pct.var, "-mergedEnrichment_OrigIdent-Facet-integratedRes.", gsub("integrated_snn_res.", "", integrated.col))
		myplot <- DimPlot(tech.integrated, 
											group.by = "orig.ident",
											split.by = integrated.col, 
											reduction = "umap", 
											pt.size = 1.5,
											ncol = round(sqrt(length(levels(tech.integrated@meta.data[[sc.col]])))),
											cols = color.palette) + 
			ggtitle(paste0(projectName, "_pctVar", pct.var, "-", integrated.col, " faceted by ", sc.col))
		plot(myplot)

		png(filename = paste0(projectName, "_pctVar", pct.var,
													"-mergedEnrichment_OrigIdent-Facet-integratedRes.", gsub("integrated_snn_res.", "", integrated.col),
													".png"),
				height = 1600, width = 1600)
		plot(myplot)
		dev.off()

@@

## map cluster ids from Seuratv1
```{r}
seurat.object@meta.data$clust.ID[rownames(seurat.object@meta.data) %in% clust3.cells] <- 3
seurat.object@meta.data$clust.ID[rownames(seurat.object@meta.data) %in% clust17.cells] <- 17
seurat.object@meta.data$clust.ID[rownames(seurat.object@meta.data) %in% clust10.cells] <- 10
seurat.object@meta.data$clust.ID[rownames(seurat.object@meta.data) %in% clust11.cells] <- 11
seurat.object@meta.data[is.na(seurat.object@meta.data)] <- 0
seurat.object@meta.data$clust.ID <- as.factor(seurat.object@meta.data$clust.ID)
```
## plot something
```{r}
DimPlot(tech.integrated, group.by = "clust.ID", split.by = "integrated_snn_res.1.5", cols = c("black", "green", "blue", "red", "orange"), ncol = 4)
```

@@

>>>>

	cluster_ids <- sort(unique(tech.integrated@meta.data[,current_res]))
	counts_df <- data.frame(matrix(nrow = length(cluster_ids), ncol = 4))
	rownames(counts_df) <- cluster_ids
	colnames(counts_df) <- c("10X", "biomark", "pct10X", "pctbiomark")
	tot.10X <- nrow(tech.integrated@meta.data[tech.integrated@meta.data$orig.ident == "10X", ])
	tot.biomark <- nrow(tech.integrated@meta.data[tech.integrated@meta.data$orig.ident == "biomark", ])
	for(id in cluster_ids){
		cell_value <- nrow(tech.integrated@meta.data[(tech.integrated@meta.data[current_res] == id) & 
																								 	(tech.integrated@meta.data$orig.ident == "10X"),])
		counts_df[id, "10X"] = cell_value
		counts_df[id, "pct10X"] = round(cell_value/tot.10X*100, 2)
		cell_value <- nrow(tech.integrated@meta.data[(tech.integrated@meta.data[current_res] == id) & 
																								 	(tech.integrated@meta.data$orig.ident == "biomark"),])
		counts_df[id, "biomark"] = cell_value
		counts_df[id, "pctbiomark"] = round(cell_value/tot.biomark*100, 2)
	}
	try(xlsx::write.xlsx(x = counts_df, 
											 file = paste0(projectName, "_pctVar", integrated.var, "_stats.xlsx"), 
											 sheetName = current_res, 
											 col.names = TRUE, 
											 row.names = TRUE, 
											 append = TRUE)
	)
	counts_df
}
```

@@

```{r}
fluor.cols <- names(mfi[, grepl("pos$", names(mfi))])
mfi.norm <- data.frame(matrix(nrow = 0, ncol = length(fluor.cols)))
colnames(mfi.norm) <- fluor.cols
for(sortdate in unique(mfi$sortdate)){
	mfi.subset <- scale(mfi[mfi$sortdate == sortdate, fluor.cols])
	mfi.norm <- rbind(mfi.norm, mfi.subset)
}
mfi.norm["pid"] <- do.call(rbind, strsplit(rownames(mfi.norm), '_'))[,3]
```
Add metadata column
```{r}
tech.integrated <- AddMetaData(tech.integrated, metadata = mfi.norm)
```
now plot some stuff
```{r}
biomark.integrated <- subset(tech.integrated, subset = orig.ident == "biomark")
```
```{r fig.height=12, fig.width=5}
RidgePlot(biomark.integrated, features = fluor.cols, cols = color.palette, ncol = 1)
```
```{r}
png(filename = paste0(projectName, "_pctVar", integrated.var, "res", integrated.res, "-fluor.png"), height = 2400, width = 800)
RidgePlot(biomark.integrated, features = fluor.cols, cols = color.palette, ncol = 1)
dev.off()
```
plot umaps
```{r}
for(integrated.col in integrated.ident.list){
		plot.title <- paste0(projectName, "_pctVar", integrated.var, "-mergedEnrichment_OrigIdent-Facet-integratedRes.", gsub("integrated_snn_res.", "", integrated.col))
		myplot <- DimPlot(tech.integrated, 
											group.by = "orig.ident",
											split.by = integrated.col, 
											reduction = "umap", 
											pt.size = 1.5,
											ncol = round(sqrt(length(levels(tech.integrated@meta.data[[sc.col]])))),
											cols = color.palette) + 
			ggtitle(paste0(projectName, "_pctVar", pct.var, "-", integrated.col, " faceted by ", sc.col))
		plot(myplot)

		png(filename = paste0(projectName, "_pctVar", integrated.var,
													"-mergedEnrichment_OrigIdent-Facet-integratedRes.", gsub("integrated_snn_res.", "", integrated.col),
													".png"),
				height = 1600, width = 1600)
		plot(myplot)
		dev.off()

@@

## map cluster ids from Seuratv1
```{r}
seurat.object@meta.data$clust.ID[rownames(seurat.object@meta.data) %in% clust3.cells] <- 3
seurat.object@meta.data$clust.ID[rownames(seurat.object@meta.data) %in% clust17.cells] <- 17
seurat.object@meta.data$clust.ID[rownames(seurat.object@meta.data) %in% clust10.cells] <- 10
seurat.object@meta.data$clust.ID[rownames(seurat.object@meta.data) %in% clust11.cells] <- 11
seurat.object@meta.data[is.na(seurat.object@meta.data)] <- 0
seurat.object@meta.data$clust.ID <- as.factor(seurat.object@meta.data$clust.ID)
```
## plot something
```{r}
DimPlot(seurat.object, group.by = "clust.ID", split.by = "integrated_snn_res.1.5", cols = c("black", "green", "blue", "red", "orange"), ncol = 4)
```

@@

```{r}
png(filename = paste0("CMP_RNA_res.1.png"), height = 800, width = 800)
DimPlot(seurat.object, group.by = "RNA_snn_res.1", cols = color.palette, pt.size = 1)
dev.off()

```{r}
